Legacy Data Confounds Modern Genomics Studies

### 2019-06-14 PlottingScripts/ProcessPlotData.Rmd

if [ ! -f $path/sig.pos.context.txt ]; then
  echo "sig pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/sig.pos.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/sig.pos.context.txt
fi 
```
Load mutation context and plot enrichment
```{r}
contextHeader = c('Chr','Pos','Ref','Alt','Flip','Context')

@@

#Chi-square test of independence
chi_test <- merge(SNP, rSNP, 
                  by = c('Start','End', 'Mut'), 
                  all =T)

chi_test$chi <- 
  (chi_test$Freq.x - chi_test$Freq.y)^2 / chi_test$Freq.y

chi_test$p_val <- pchisq(chi_test$chi, 
                         df=96, 
                         lower.tail=FALSE)

SNP <- merge(SNP, 
             chi_test %>% 
               select(c('Start','End', 'Mut',
                        'chi', 'p_val')), 
             by = c('Start','End', 'Mut'))

>>>>

if [ ! -f $path/sig.pos.context.txt ]; then
  echo "sig pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/sig.pos.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/sig.pos.context.txt
fi 
```

extract context for GCAT test snps of interest
```{bash}
#Using GenomeWide.AncestralContext.txt
#To get mutation context, use $path/AncestralContext.py
#compare first two columns in both files, extract matches
path='/Users/luke/Documents/LegacyData/LatexManuscript/SupplementaryData/'

if [ ! -f $path/gcat.sig.pos.context.txt ]; then
  echo "sig pos context"
  awk 'NR==FNR{a[$1,$2];next} ($1,$2) in a' \
  $path/Significant_Positions.txt \
  $path/GenomeWide.AncestralContext.txt \
  > $path/gcat.sig.pos.context.txtt
fi 
```

Load mutation context and plot enrichment
```{r}
contextHeader = c('Chr','Pos','Ref','Alt','Flip','Context')

@@

#chi-squared contingency table tests
chi_test <- merge(SNP, rSNP, 
                  by = c('Start','End', 'Mut'), 
                  all =T)

chi_test[is.na(chi_test)] <- 0

chi_test$chi_p <- 
  lapply(split(chi_test %>% 
                 select(Freq.x,Freq.y), 
               (1:nrow(chi_test) - 1)), 
         function(data) 
           chisq.test(data)$p.value)

SNP <- merge(SNP, 
             chi_test %>% 
               select(c('Start','End', 'Mut','chi_p')), 
             by = c('Start','End', 'Mut'))
